Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-13 figures.Rmd
remove 5.8 lactate from UM and lactate data for HV in table 1

# Age, hematocrit, and lactate
df_hbox %>%

@@

  dplyr::rename(" " = "variable",
                "Healthy volunteers (HV)" = "HV",
                "Uncomplicated malaria (UM) patients" = "UM",
                "Cerebral malaria (CM) patients" = "CM") %>% 
  knitr::kable(align = rep('c', 4))

```
**Table 1.** A summary of subject information and hematological data. Group patient data presented as median (range). Note: sex not recorded for 3 CM patients.

>>>>

# Age, hematocrit, and lactate
df_clinical_res <- df_hbox %>%

  dplyr::filter(Subject.ID..NIAID. != "TM1018") %>%

@@

  dplyr::rename(" " = "variable",
                "Healthy volunteers (HV)" = "HV",
                "Uncomplicated malaria (UM) patients" = "UM",
                "Cerebral malaria (CM) patients" = "CM")

  # remove lactate data for HV
  df_clinical_res[11,]$`Healthy volunteers (HV)` <- "--"

  # create kable df
  df_clinical_res %>% knitr::kable(align = rep('c', 4))

```
**Table 1.** A summary of subject information and hematological data. Group patient data presented as median (range). Note: Sex not recorded for 3 CM patients; Lactate data removed for HV due to inconsistent data.
